\speculake: Hiding Malware in Speculative Execution

### 2018-05-08 paper/abstract.tex
abstract pass

We introduce \emph{\speculake}, which compiles arbitrary malicious code into a
seemingly-benign payload binary. When a separate trigger program performs a specific
pattern of indirect jumps, it (mis)trains the CPU's branch predictor. Subsequent
executions of the payload binary with similar jumps causes the CPU to mispredict its
branches and speculatively execute a malicious payload, which communicates
results back to the real world via side channels.

@@

Finally, we describe defenses, but in all honesty, you're probably not going to like
them.

We consider this to be a new thrust in attack vector research that harkens to work 
done on hardware red-pills and weird machines. We demonstrate that unintended 
functionality of architechture can be used to compose malicious programs with 
new and different properties. This technique poses novel and unique challenges for 
malware modeling efforts, as it forces an environment to either
faithfully reproduce all hardware behaviors, or overcome a much larger burden of 
reverse engineering.

>>>>

We introduce \emph{\speculake}, which compiles arbitrary malicious code into a
seemingly-benign payload binary. When a separate trigger program runs on the same
machine, it mistrains the CPU's branch predictor, causing the payload program to
\emph{speculatively} execute code, and communicating its results back to the
rest of the payload program, changing its behavior.

@@

%Finally, we describe defenses, but in all honesty, you're probably not going to like
%them.

\speculake demonstrates a new kind of malware that evades existing reverse
engineering and binary analysis techniques. Because its true functionality can be
contained in seemingly unreachable dead code, and its control flow driven
externally by any other program running at the same time, \speculake poses a
novel threat to state-of-the-art malware analysis techniques.

%We consider this to be a new thrust in attack vector research that harkens to work 
%done on hardware red-pills and weird machines. We demonstrate that unintended 
%functionality of architechture can be used to compose malicious programs with 
%new and different properties. This technique poses novel and unique challenges for 
%malware modeling efforts, as it forces an environment to either
%faithfully reproduce all hardware behaviors, or overcome a much larger burden of 
%reverse engineering.
